# Importing the gating template 

Here we assume that you have a flowjo workspace consisting of at least 1 sample which is gated. 

Using `open_flowjo_xml` you are importing the flowjo workspace into R.
The arg `name=1` meaning that it only imports the first sample into R
this function is from CytoML
Currently, the best way to download CytoML (without the docker image)
is through bioconductor. However, this limits us in terms of exporting
the gating set (gs) from R to flowjo.
```{r,echo=T,eval=F}
library(flowWorkspace)
library(openCyto)
library(CytoML)
library(ggcyto)
library(grid)
library(gridExtra)
setwd('C:\Users\Kei Onn\Desktop\pipeline_masscytof_latest')
wsp <- list.files(".", pattern = "test09-Apr-2025.wsp$")
ws<-open_flowjo_xml(paste0(getwd(), "/", wsp), name = 1, sample_names_from = "sampleNode")
```


## Visualisation

Here we need a sanity check to see that the gating template which you imported
from flowjo is not empty!
Again I am only creating a gating set (which is synonymous as your group gating template in flowjo) so name=1
```{r,echo=T,eval=F}
gs <- flowjo_to_gatingset(ws, name = 1,emptyValue = FALSE)
par(mar = c(4, 4, .1, .1))
plot(gs)

```

```{r,echo=F,eval=T}
suppressMessages(library(png))
img1_path <- 'C:/Users/Kei Onn/Desktop/local_preparreddata/verivswithoutvericells/gatingH_WITHOUTveri.png'
img1 <- readPNG(img1_path, native = TRUE, info = TRUE)
knitr::include_graphics(img1_path)
```

