# Applying gates to your fcs file paths
Here we will be applying the gate you created
using `flowjo_to_gatingset()` to the fcs file paths of your interest. 
Again I am selecting `gs[[1]]` meaning the first sample of my gating set

```{r,eval=F,echo=T}
gating_applied<-flowWorkspace::gh_apply_to_new_fcs(gs[[1]], all_files,emptyValue=F)
```

Here we are checking the output of a single fcs file after applying the gate
```{r,echo=T,eval=F}
gs_pop_get_count_with_meta(gating_applied[[1]],'freq')
res<-autoplot(gating_applied[[1]])
qcp <- ggcyto_arrange(res, nrow = 5)
```

```{r,echo=F,eval=T}
suppressMessages(library(png))
img1_path <- 'C:/Users/Kei Onn/Desktop/local_preparreddata/manualvsbatchcomp/gatingstrategy_WITHOUTveri.png'
img1 <- readPNG(img1_path, native = TRUE, info = TRUE)
knitr::include_graphics(img1_path)
```


And finally.. we are doing the loop for all files
Note that for here I am extracting the population statistics via
`gs_pop_get_count_with_meta()` for flowWorkspace, the argument `freq`
refers to freq against all the cells, and not just the direct parent population(unlike flowjo).
Therefore, i usually retrieve `count`instead and normalize against my parent of interest
```{r,echo=T,eval=F}
pop_stats_df_list <- list()

#replace with any title you want

pdf("all_gating_qc_plots_WITHOUTVERI.pdf", width = 12, height = 8)

for (i in seq_along(gating_applied)) {
  
  gs <- gating_applied[[i]]
  sample_name <- sampleNames(gs)[1]
  
  
  res <- autoplot(gs)
  qcp <- ggcyto_arrange(res, nrow = 5)
  
  grid.newpage()
  grid.text(sample_name, x = 0.5, y = 0.98, gp = gpar(fontsize = 16, fontface = "bold"))
  pushViewport(viewport(y = 0.45, height = 0.9))
  grid.draw(qcp)
  popViewport()
  
  pop_stats_i <- as.data.frame(gs_pop_get_count_with_meta(gs, "count"))
  pop_stats_df_list[[i]] <- pop_stats_i
}

dev.off()
names(pop_stats_df_list)<-sampleNames(gating_applied)
```

conversion to dataframe
```{r,eval=F,echo=T}
pop_stats_df<-imap_dfr(pop_stats_df_list, ~ mutate(.x, Sample = .y))
head(pop_stats_df)
```

Annd... thats it!
I think it really important to QC the output from the pdf where you can eyeball if there is any weird discrepancies from the batch gating.
Also to note, sometimes there may be sample to sample variation so if the gates doesnt work, we need to refine them from the wsp. 

